R package qshift: A functional programming approach to shifted probability

### 2016-09-21 docs/qshift-article/article.Rmd
revisione nomenclatura articolo shift

```{r max_likelihood_est}
ltweibull <- function(x){
  # starting values for parameters (scale, shape) and shift
  shift <- min(x) - 0.01
  x1 <- x - shift
  shape <- (sd(x1)/mean(x1))^(-1.086)
  scale <- mean(x1)/gamma(1+1/shape)
  # parameters vector definition
  theta <- c(shape, scale, shift)
  # likelihood function
  ll <- function(theta, x){
    shape <- theta[1]
    scale <- theta[2]
    shift <- theta[3]
    ld <- dsweibull(x = x, shape = shape, scale = scale, shift = shift, log = TRUE)
    -sum(ld)
  } 
  # maximum likelihood estimation
  optim(par = theta, fn = ll, x = x)[["par"]]
}
```

@@

# maximum likelihood estimate for the shifted weibull distribution
ltweibull(x = x)
```

>>>>

```{r max_likelihood_est}
lsweibull <- function(x){
  # starting values for parameters (scale, shape) and shift
  shift <- min(x) - 0.01
  x1 <- x - shift
  shape <- (sd(x1)/mean(x1))^(-1.086)
  scale <- mean(x1)/gamma(1+1/shape)
  # parameters vector definition
  theta <- c(shape, scale, shift)
  # likelihood function
  ll <- function(theta, x){
    shape <- theta[1]
    scale <- theta[2]
    shift <- theta[3]
    ld <- dsweibull(x = x, shape = shape, scale = scale, shift = shift, log = TRUE)
    -sum(ld)
  } 
  # maximum likelihood estimation
  optim(par = theta, fn = ll, x = x)[["par"]]
}
```

@@

# maximum likelihood estimate for the shifted weibull distribution
lsweibull(x = x)
```
